Transcriptomic Analysis of Expressions of Biomarkers and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-25 Cover_letter_JPM.tex
Updates from Overleaf

We appreciate the reviewer for the critical comments.
 %=> includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
A group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
In the data science literature, feature selection has been usually applied for a group of genes which are contributing as independent variables for building model such as logistic regression. %The dependent variables are the survival data.
%Scientists are often interested in selecting certain genes that are related to a categorical response variable, such as the onset or progression of cancer. These genes are known as signatures in the life sciences literature; for the purposes of our paper, we will call them features.
Least Absolute Shrinkage and Selection Operation (LASSO):
The feature selection (subsets of gene) could be done by the $L_{1}$-regularized path algorithm in LASSO regression. That is suggested by Branders and his colleagues\cite{Branders2014} applying on those high-dimensional data i.e., twenty thousands of features (genes) and only hundreds of sample size.
LASSO is suitable at picking up a small signal (gene signature) through lots of noise (all protein-coding genes).
% R code by https://www4.stat.ncsu.edu/~post/josh/LASSO_Ridge_Elastic_Net_-_Examples.html

% feature selection by lasso (L1 regularization)
% LASSO, shrinkage coefficients to zero, for selection the features
Cross-validation is perhaps the simplest and most widely used method for select one of models at specific \lambda. % k-fold Cross-validation
As the coefficients of logistic regression are reduced to zero by LASSO, the useless features associated with those coefficients will be omitted.
The important features that contribute much to the model will be selected.
Cross-validation error is calculated to find the optimal value of the regularization rate (i.e., lambda, \lambda). \lambda could control the size of a small amount of bias.
% over-fitting causes problem
During fitting of logistic model, it is necessary to add that small amount of bias for getting a significant drop in the variance to prevent it's over-fitting.  
%(over-fitting is called high-variance)
In case with over-fitting, this trained model will only perfect match every individual cases, while has higher variability to predict what it never see.
Over-fitting could be controlled well by using both LASSO $L_{1}$-regularization and cross validation.

%RLassoCox\\
We utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://\\github.com/weiliu123/RLassoCox) for training the Cox proportional hazard regression and multinomial logistic regression models in gene expression analysis to identify a group of genes that contribute to the survival outcome of HNSCC patient. %and gene interaction networks (The KEGG network\cite{Simon2011}).
% data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.
% based on gene expression profiles,
The Cox and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
The RLassoCox make use of both tasks for gene-expression based survival analysis.

% medium: https://towardsdatascience.com/regularization-machine-learning-891e9a62c58d

@@

% **** [2021/06/22] by Bayes_survival.R
The results shows
%[line 403] cv.mod <- cvRLassoCox(x=x.train, y=y.train, globalGraph=dGMMirGraph, nfolds = 10) 
#Calculating Cox p-value...Done [2021/06/22] 19:42
#Performing directed random walk...Done
#Performing cv.glmnet...Done
#code inside: fit.lasso <- glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
%Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
% Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
the selected features (62 genes) are selected by their (non-zero) coefficients. 
%cv.mod.candidate 62 genes 
However, they are not performed well either in GSE65858 HNSCC or TCGA HNSCC (please see Figure \ref{fig:Bayes62}).\\

@@

%\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}
\bibliographystyle{unsrt} %model1-num-names}
\bibliography{TCGA_margin_cutoff.bib}

>>>>

We appreciate the reviewer for the critical comments.
 %=> includes gene signature that are related to a grouping structures with similar biological functions tend to have similar expressions. 
Since we have tried to integrate multiple genes in survival analysis, a group of co-regulated genes that are preferable to be taken into consideration in a gene signature.
Searching about the data science literature, feature selection has been usually applied for a group of genes which are contributing as independent variables for building model such as logistic regression. %The dependent variables are the survival data.
%Scientists are often interested in selecting certain genes that are related to a categorical response variable, such as the onset or progression of cancer. These genes are known as signatures in the life sciences literature; for the purposes of our paper, we will call them features.
%Least Absolute Shrinkage and Selection Operation (LASSO):
Branders and his colleagues\cite{Branders2014} have suggested that regularization of regression model should be applied on analysis of the high-dimensional data, i.e. twenty thousands of features (genes) and only hundreds of sample size.
The $L_{1}$-regularized path algorithm by Least Absolute Shrinkage and Selection Operation (LASSO) regression could perform feature selection (a subset of gene).
LASSO is suitable at picking up a small signal (gene signature) through lots of noise (twenty thousands of protein-coding genes).
% R code by https://www4.stat.ncsu.edu/~post/josh/LASSO_Ridge_Elastic_Net_-_Examples.html
Our approach is to build a logistic regression model for the prediction of patient's survival.
% over-fitting causes problem
% During fitting of logistic model, 
Beside feature selection,
it is also necessary to add that small amount of bias (lambda, $\lambda$) for getting a significant drop in the variance to prevent over-fitting of the model.
$\lambda$ could control the amount of bias dealing with over-fitting.
%(over-fitting is called high-variance)
In such a case, over-fitted model will only perfectly match every individual cases, and has higher variability to predict what it never see.
Over-fitting will limit usefulness of the model in it's generalization, and could be controlled well by using both LASSO $L_{1}$-regularization and cross validation.
% feature selection by lasso (L1 regularization)
% LASSO, shrinkage coefficients to zero, for selection the features
% perhaps the simplest and 
Cross-validation error is calculated to find the optimal value of $\lambda$.
%Cross-validation is most widely used method for select one of models at specific regularization rate (i.e. lambda, \lambda) during the model fitting.
% k-fold Cross-validation
As the coefficients of logistic regression are reduced to zero by LASSO, %the useless features (genes) associated with those coefficients will be omitted.
the important features that contribute much to the model will be selected under that optimal value of $\lambda$.

% multinomial
%RLassoCox\\
We have utilized the RLassoCox\cite{Simon2011}\cite{Liu2021} (RLasso-Cox model, implemented in a bioconductor package, available at https://github.com/weiliu123/\\RLassoCox) for training the Cox proportional hazard regression and logistic regression models in gene expression analysis to identify a group of genes that contribute to survival outcome of HNSCC patient. 
%and gene interaction networks (The KEGG network\cite{Simon2011}).
% data(dGMMirGraph) # The KEGG network constructed by the R package iSubpathwayMiner.
% based on gene expression profiles,
%The Cox and logistic regression are standard models for their respective tasks: either fitting survival times or classifying samples.
The RLassoCox make use of both Cox and LASSO logistic regression for gene-expression based survival analysis.
The model training has been performed under 10-fold cross-validation.
% medium: https://towardsdatascience.com/regularization-machine-learning-891e9a62c58d

@@

% **** [2021/06/22] by Bayes_survival.R
The results shows
% k-fold Cross-validation
%[line 403] cv.mod <- cvRLassoCox(x=x.train, y=y.train, globalGraph=dGMMirGraph, nfolds = 10) 
#Calculating Cox p-value...Done [2021/06/22] 19:42
#Performing directed random walk...Done
#Performing cv.glmnet...Done
#code inside: fit.lasso <- cv.glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
%Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
% Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
the selected features (62 genes) are selected by their (non-zero) coefficients. 
%cv.mod.candidate has 62 genes 
However, they are performed poor either in GSE65858 HNSCC or TCGA HNSCC (please see Figure \ref{fig:Bayes62}).\\

@@

%\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}
\bibliographystyle{unsrt} %model1-num-names}
\bibliography{TCGA_margin_cutoff.bib, Deep_Learning.bib}
